The Adaptive Multi-scale Simulation Infrastructure - Design and Application

### 2016-01-10 doc/articles/amsi_biotissue/paper.tex
more paper work

@@

\label{amsi_scales}
A configuration file is supplied during command invocation containing the initial configuration of the process sets and their assignment to individual scales, as well as declaring the coupling between scales in the simulation. The declaration of a scale and the initialization of the process set associated with the scale are considered a single atomic operation in the current implementation. A simple configuration file can be seen in listing \ref{amsi config file} which declares the existence of two scales, macro and micro\_fo, and assigns them 64 and 8128 processes respectively (for a total of $2^13$ processes). The file also specifies the scale-coupling relations, with macro coupled to micro and micro coupled to macro. Note that the order of specification is not relevant to the operation of amsi.
%
\begin{lstlisting}
  macro 64
  micro_fo 8128
  #
  macro micro_fo
  micro_fo macro_fo
\end{lstlisting}
\label{amsi config file}
%

@@

The incremental displacements (deltas generated by the previous Newton-Raphson iteration) on each engineering-scale finite element node are used to distort the a dimensionless representative volume element (RVE) through a dimensionalized abstraction of the RVE embedded in the engineering domain and an associated displacement mapping term $\frac{d\mathbf{RVE}}{d\mathbf{FE}}$, the first order relation between the incremental displacement of an RVE with respect to the displacement of the associated mesh element. This results in each micro-scale node being displaced. Each RVE is a dimensionless unit cube containing a connected collagen fiber network, for the present results the fibers are implemented as truss elements and their distribution is generated using Delauney triangulation. The micro-scale boundary condition necessitates that the force exerted by each fiber network node located on the boundary of the RVE be zero. The micro-scale global Jacobian is formulated along with the force vector, wherein the boundary condition is enforced by setting specific rows of the force vector associated with boundary nodes to zero.

@@

\section{Results and Discussion}\label{results}
The biotissue simulation was run on the AMOS BG/Q machine housed at the CCI facilities. Both strong and weak scaling studies were conducted up to an eighth of the total machine core count, or 16384 cores. The ratio of macro-scale to micro-scale assigned processes was held near 1:128, though the total core count was kept as an integer power of 2 in order for the SLURM job scheduler to submit the jobs to the compute nodes in a timely manner. The precise calculation used to determine macro and micro ratio is given by 
%
\begin{lstlisting}[Language=C]
  num_cores = 128 * num_macro;
  num_micro = num_core - num_macro;
\end{lstliting}
\label{macro micro ratio}
%
thus as the number of cores assigned to the macro-scale computation increases, the ratio approaches 1:128.

>>>>

\lstset{basicstyle=\small, 
        stringstyle=\ttfamily, 
        frame=top, frame=bottom,
        captionpos=t}

@@

\label{amsi_scales}
A configuration file is supplied during command invocation containing the initial configuration of the process sets and their assignment to individual scales, as well as declaring the coupling between scales in the simulation. The declaration of a scale and the initialization of the process set associated with the scale are considered a single atomic operation in the current implementation. A simple configuration file can be seen in listing \ref{amsi_config_file} which declares the existence of two scales, macro and micro\_fo, and tells the amsi intialization procedures to assigne them process sets containig 64 and 8128 processes, respectively (for a total of $2^{13}$ processes). The file also specifies the scale-coupling relations, with macro coupled to micro and micro coupled to macro. Note that the order of specification is not relevant to the operation of amsi.
%
\begin{lstlisting}[caption={amsi\_config file},label=amsi_config_file]
  macro 64
  micro_fo 8128
  #
  macro micro_fo
  micro_fo macro_fo
\end{lstlisting}
%
Typically creation of this file will be automated and added to the shell script used to invoke the simulation, so ensure that process counts passed in throught the configuration file are valid. Alternative specification mechanisms such as ratio specification (equivalently percentage specification) are being considered for future use to prevent the possbility of misallocation of processes (the user not specifying assignment for all processes available to the simulation).

@@

The incremental displacements (deltas generated by the previous Newton-Raphson iteration) on each engineering-scale finite element node are used to distort the a dimensionless representative volume element (RVE) through a dimensionalized abstraction of the RVE embedded in the engineering domain and an associated displacement mapping term $\frac{d\mathbf{RVE}}{d\mathbf{FE}}$, the first order relation between the incremental displacement of an RVE with respect to the displacement of the associated mesh element. This results in each micro-scale node being displaced. Each RVE is a dimensionless unit cube containing a connected collagen fiber network, for the present results the fibers are implemented as truss elements and their distribution is generated using Delauney triangulation, resulting in a high coordination number at each node and consequently a numerically stable fiber network. The micro-scale boundary condition necessitates that the force exerted by each fiber network node located on the boundary of the RVE be zero. The micro-scale global Jacobian is formulated along with the force vector, wherein the boundary condition is enforced by setting specific rows of the force vector associated with boundary nodes to zero.

@@

\section{Results and Discussion}\label{results}
The biotissue simulation was run on the AMOS BG/Q machine housed at the CCI facilities. Both strong and weak scaling studies were conducted up to an eighth of the total machine core count, or 16384 cores. The ratio of macro-scale to micro-scale assigned processes was held near 1:128, though the total core count was kept as an integer power of 2 in order for the SLURM job scheduler to submit the jobs to the compute nodes in a timely manner. The precise calculation used to determine macro and micro process counts is given by 
%
\begin{lstlisting}[language=Bash,caption={process assignment calculation}]
  MICRO_RATIO=128
  NP=$(( $NUM_MACRO * $MICRO_RATIO))
  NUM_MICRO=$(( $NP - $NUM_MACRO))
\end{lstlisting}
\label{macro micro ratio}
%
thus as the number of cores assigned to the macro-scale computation increases, the ratio approaches 1:128.
